---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AssetAllocation

<!-- badges: start -->
<!-- badges: end -->

The goal of AssetAllocation is to perform backtesting of asset allocation strategies. The main functions that the user interacts with is backtest_allocation().  

## Installation

You can install the development version of AssetAllocation from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rubetron/AssetAllocation")
```

## Example

Simple example using preloaded strategy:

```{r example1}
library(AssetAllocation)
## Example 1: backtesting one of the asset allocations in the package
us_60_40 <- basic_asset_alloc$us_60_40

# test using the data set provided in the package
bt_us_60_40 <- backtest_allocation(us_60_40, ETFs_daily)

# plot returns
library(PerformanceAnalytics)
chart.CumReturns(bt_us_60_40$returns,
                 main = paste0("Backtest of the ",
                               bt_us_60_40$strat$name,
                               " portfolio"),
                 ylab = "Cumulative returns"
)

# show table with performance metrics
bt_us_60_40$table_performance


```


Another example creating a strategy from scratch, retrieving data from Yahoo Finance, and backtesting: 
```{r example2}
library(AssetAllocation)
# create a strategy that invests equally in momentum (MTUM), value (VLUE), low volatility (USMV) and quality (QUAL) ETFs.

factor_strat  <- list(name = "EW Factors",
                      tickers = c("MTUM", "VLUE", "USMV", "QUAL"),
                      default_weights = c(0.25, 0.25, 0.25, 0.25),
                      rebalance_frequency = "month",
                      portfolio_rule_fn = "identity")

# get data for tickers using getSymbols
returns_ETFs <- get_return_data_from_tickers(factor_strat$tickers, starting_date = "2013-08-01")

# backtest the strategy
bt_factor_strat <- backtest_allocation(factor_strat,
                                       returns_ETFs)

# plot returns
library(PerformanceAnalytics)
chart.CumReturns(bt_factor_strat$returns,
                 main = paste0("Cumulative returns of the ",
                               bt_factor_strat$strat$name,
                               " portfolio"),
                 ylab = "Cumulative returns"
)

# show table with performance metrics
bt_factor_strat$table_performance
```

